Knowledge \& the web: exercise session 6

### 2015-11-22 exercise_6/ex6.tex
decision tree

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: exercise session 6}
\begin{document}
\maketitle
In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
To train the classification models, we use the information about passengers with passengerId 1 until 800 as our training data. The test data for evaluating each classification model consists of the passengers with ids 801 until 891.

@@

\section{Decision trees}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{svg}
\usepackage{float}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: exercise session 6}
\begin{document}
\maketitle
In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
To train the classification models, we use the information about passengers with passengerId 1 until 800 as our training data. The test data for evaluating each classification model consists of the passengers with ids 801 until 891.

@@

\section{Decision trees}
Apart from \emph{rule learning} we also experimented witch decision trees. First we applied the standard decision tree in RapidMiner, it created a to complicated decision tree, as you can see in figure 1.
\begin{figure}[H]
  \centering
  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
  \caption{Original decision tree with maximal depth of 20}
\end{figure}
Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
\begin{figure}[H]
  \centering
  \includesvg[width = 1\textwidth]{decisiontreetitanic}
  \caption{Decision tree with maximal depth of 3}
\end{figure}
